\Title

### 2021-01-25 manuscript/manuscript.tex
Review the text about source layout results

Our first goal is to to compare the performance of all source distributions
from Table~\ref{tab:source-distributions} when predicting harmonic field data
using the equivalent sources technique.
To do so we have created a synthetic model made out of prisms of different
shape and density contrasts.
The gravitational effect of this synthetic model have been computed on
a regular grid (\emph{target} grid) at a constant height and on two different
set of observation points that we will call \emph{synthetic surveys}: a ground
and an airborne survey.
The data from each synthetic survey is interpolated on the points of the
\emph{target} grid and then scored against its values.
We can then quantitatively compare how accurate is each source distribution at
predicting unobserved data on each synthetic survey and quantify the
computational load needed to do it.

Each source distribution from Table~\ref{tab:source-distributions} needs
certain parameters in order to build the set of point sources.
The prediction capabilities of the source distribution depends on the choice of
these parameters.
For example, locating the sources beneath the data points at constant depth
needs the definition of the \emph{depth} parameter.
If the sources are set too close to the data points, the source distribution
it's very likely to over-fit the data: the measured field will be recovered, but
the predictions on unobserved locations will be very inaccurate.
Another parameter that plays an important role on the predictive capabilities
of the sources is the \emph{damping}.

On real world scenarios, choosing the values of the parameters is a challenging
task: it's not easy to determine the accuracy of the predictions without
knowing the true value of the field on unobserved locations.
This problem can be solved through cross-validation.
When working with a synthetic model, the situation is different: we can compute
the true values of harmonic field generated by the synthetic model on any
point.
Therefore, interpolating the observed data on the same points of the
\emph{target} grid and then scoring the prediction against the true values of
the \emph{target} grid constitutes an objective way to measure the predictive
accuracy of the source distribution.

In order to compare the predictive capabilities of each source distribution we
perform a parameter search to obtain the best prediction that can be achieved
by each one of them.
For each source distribution we proposed different values for each parameter
(see Tables~\ref{tab:parameters-ground-survey}
and~\ref{tab:parameters-airborne-survey}).
These parameters values are combined obtaining several \emph{set of
parameters}.
We use each set of parameters to create the sources, fit their coefficients
through least-squares and predict the field on the same points of the
\emph{target} grid.
We then \emph{score} the prediction by computing the root mean square (RMS)
between the prediction and the true values of the \emph{target} grid.
Finally, we obtain the \emph{best prediction} for each source distribution as
the one that achieves the lowest RMS.
This process is carried out on both ground and airborne synthetic surveys.
See Algorithm~\ref{alg:source_distributions_comparison} for a concise
representation of it.

\begin{algorithm}[!h]
  \DontPrintSemicolon
  \setstretch{1.5}

  define possible values for each parameter
  \;

  generate each possible combination of parameters values: obtain several
  \emph{sets of parameters}
  \;

  \For{each set of parameters}{

    select the $M$ locations of the equivalent sources
    \;

    estimate the source coefficients
    \;

    predict field values on target grid points
    \;

    calculate the RMS between the predictions and the target grid
    \;
  }

  the best set of parameters produces the smallest RMS
  \;

  \BlankLine
  \setstretch{1}
  \caption{Algorithm for estimating the best prediction using synthetic data.}
  \label{alg:source_distributions_comparison}
\end{algorithm}

Tables~\ref{tab:parameters-ground-survey}
and~\ref{tab:parameters-airborne-survey} also show the parameter combination
that produces the best prediction for each source distribution and its
corresponding RMS score, for both ground and airborne synthetic surveys,
respectively.
Figures~\ref{fig:ground-survey-differences}
and~\ref{fig:airborne-survey-differences} show the differences between the
target grid and the best prediction achieved by each source distribution, for
both ground and airborne synthetic surveys, respectively.

\begin{figure*}
    \includegraphics[width=\linewidth]{figs/ground_survey_differences.pdf}
    \caption{
        Differences between gravitational effects measured on the target grid
        and the ones produced by the best prediction made by each source
        distribution based on the synthetic ground survey.
    }
    \label{fig:ground-survey-differences}
\end{figure*}

\begin{figure*}
    \includegraphics[width=\linewidth]{figs/airborne_survey_differences.pdf}
    \caption{
        Differences between gravitational effects measured on the target grid
        and the ones produced by the best prediction made by each source
        distribution based on the synthetic airborne survey.
    }
    \label{fig:airborne-survey-differences}
\end{figure*}

@@

We are indebted to the developers and maintainers of the open-source software
without which this work would not have been possible.

The synthetic airborne survey was based upon the Great Britain aeromagnetic
data, reproduced with the permission of the British Geological Survey
$\textcopyright$UKRI\@.
All rights reserved.

>>>>

Each source distribution strategy requires certain hyper-parameters to be
chosen in order to build the set of point sources.
For example, using a constant depth needs the definition of the depth and using
block-average-sources requires the definition of the block size.
The predictive capabilities of the equivalent sources depend on the choice of
these hyper-parameters.
To ensure that our comparisons are fair, we perform an exhaustive search over
combinations of hyper-parameter values (including the damping parameter from
Eq.~\ref{eq:misfit}) to obtain the best prediction that can be achieved by each
source distribution strategy.
Here, the best prediction is defined as the one that minimizes the root
mean-square error (RMS) between interpolated values and the target grid
(Fig.~\ref{fig:synthetic-target}).
The parameter values used in these searches and the one producing the smallest
RMS error are outlined in Tables~\ref{tab:parameters-ground-survey}
and~\ref{tab:parameters-airborne-survey}.

Figures~\ref{fig:ground-survey-differences}
and~\ref{fig:airborne-survey-differences} show the differences between the
target grid and the best prediction achieved by each source distribution
strategy for the ground and airborne synthetic surveys, respectively.
For the synthetic ground survey, the horizontal layouts produced similar RMS
values of appropriately 0.8 mGal regardless of the depth type, with the
exception of the regular-grid layout which produced a larger RMS of
\BestGroundGridSourcesConstantDepthRms{} mGal.
The differences between the target grid and the interpolated values are larger
in regions of poor data coverage.
Edge effects are present for all strategies but are noticeably smaller for the
combination of block-averaged-sources with a variable depth based on the
nearest neighbour distance.
For the synthetic airborne survey, all strategies (including the regular-grid)
produced similar RMS errors of approximately 0.3 mGal.
The maps of the differences between the target grid and interpolation results
are visually indistinguishable from each other.

\begin{figure*}
    \includegraphics[width=\linewidth]{figs/ground_survey_differences.pdf}
    \caption{
        Pseudo-color maps of the differences between the target grid and the
        interpolated synthetic ground survey data produced by each source
        distribution strategy.
        The black dots represent the horizontal location of the synthetic data
        points. The RMS error and total number of equivalent sources is
        reported for each strategy at the top of the respective maps.
    }
    \label{fig:ground-survey-differences}
\end{figure*}

\begin{figure*}
    \includegraphics[width=\linewidth]{figs/airborne_survey_differences.pdf}
    \caption{
        Pseudo-color maps of the differences between the target grid and the
        interpolated synthetic airborne survey data produced by each source
        distribution strategy.
        The black dots represent the horizontal location of the synthetic data
        points. The RMS error and total number of equivalent sources is
        reported for each strategy at the top of the respective maps.
    }
    \label{fig:airborne-survey-differences}
\end{figure*}

@@

We are indebted to the developers and maintainers of the open-source software
without which this work would not have been possible.
The synthetic airborne survey was based upon the Great Britain aeromagnetic
data, reproduced with the permission of the British Geological Survey
\textcopyright{} UKRI.
All rights reserved.
